Network Deliberation: The role of network structure in large-scale, internet-enabled, participatory decision-making

### 2022-08-19 UMich/chapters/ch03-NetDelibABM.tex
Final version accepted by UMich.
Fix typos.

The simulation begins at time $t=0$ by generating a set of initial solutions $s_{v,0}$ for the agents.
These are generated randomly, with each possible solution having equal probability.
The simulation proceeds iteratively.
At time $t$ each agent applies one of several {\em learning strategies}, to determine its preferred solution at time $t+1$.
Learning strategies can rely on the agent's own solution, the solutions of its neighbors, and potentially additional information shared by its neighbors.
Learning strategies may also incorporate information about the objective function, modeling an agents' ability to evaluate the quality of solutions.
To allow for ties, learning strategies produce a set of solutions rather than a single solution.
In our simulations, we choose winners at random in the case of a tie.
We present results for 1000 randomly generated NK model objectives.
with each network/strategy combination simulated once per objective function.
In keeping with other authors \cite{barkoczi_social_2016, lazer_network_2007} we use $N=15$ and $K=6$.
We allow each simulation to proceed for 300 iterations, which we have found sufficient to guarantee convergence with our chosen parameters.
For real-world comparison, on average, an active English-language Wikipedia editor makes about 45 edits per month \cite{noauthor_wikipediastatistics_2022}.

@@

One of the strongest capabilities an agent might posses, is to compare two arbitrary solutions to determine which yields a higher value of the objective function. We represent this capability using the {\em arbitrary comparison} oracle.
\begin{definition}
The arbitrary comparison oracle $\mathcal{O^>}(s_1, s_2)$ is given by:
\begin{eqnarray}
\mathcal{O}^>(s_1, s_2) &\equiv&
Q(s_1) > Q(s_2)
\end{eqnarray}
\end{definition}

>>>>

The simulation begins at time $t=0$ by generating a set of initial solutions $s_{v,0}$ for the agents.
These are generated randomly, with each possible solution having equal probability.
The simulation proceeds iteratively.
At time $t$ each agent applies one of several {\em learning strategies}, to determine its preferred solution at time $t+1$.
Learning strategies can rely on the agent's own solution, the solutions of its neighbors, and potentially additional information shared by its neighbors.
Learning strategies may also incorporate information about the objective function, modeling an agents' ability to evaluate the quality of solutions.
To allow for ties, learning strategies produce a set of solutions rather than a single solution.
In our simulations, we choose winners at random in the case of a tie.
We present results for 1000 randomly generated NK model objectives.
with each network/strategy combination simulated once per objective function.
In keeping with other authors \cite{barkoczi_social_2016, lazer_network_2007} we use $N=15$ and $K=6$.
We allow each simulation to proceed for 300 iterations, which we have found sufficient to guarantee convergence with our chosen parameters.

@@

One of the strongest capabilities an agent might posess, is to compare two arbitrary solutions to determine which yields a higher value of the objective function. We represent this capability using the {\em arbitrary comparison} oracle.
\begin{definition}
The arbitrary comparison oracle $\mathcal{O^>}(s_1, s_2)$ is given by:
\begin{eqnarray}
\mathcal{O}^>(s_1, s_2) &\equiv&
Q(s_1) > Q(s_2)
\end{eqnarray}
\end{definition}

### 2022-08-19 UMich/front_materials/abstract.tex
Fix typos.

As groups grow in size, they gain access to additional resources, creating opportunities for collective intelligence and collective action.
However, at very large scales, group decision-making becomes prohibitively slow and difficult to coordinate.
Traditional solutions include representative decision-making and/or a shift from deliberation to voting.
Both approaches sacrifice desirable properties.
Representative decision-making loses the potential benefits of collective intelligence and introduces hierarchies that may place the interests of specific individuals ahead of the interests of the group.
Voting sacrifices generativity: allowing a choice between predefined options, without allowing for improvement to those options.
Arrow’s impossibility theorem also fundamentally limits the fairness of voting.
This project proposes Networked Deliberation as a potential means of effective large-scale decision-making.
In Networked Deliberation, members of a large group are repeatedly partitioned into small deliberative pods.
Overlap between pods at different stages enables group-wide diffusion of information and preferences.
Different methods for assigning members to pods result in different network topologies.
This work combines observational study, agent-based modeling, and an experiment to evaluate and better understand network deliberation.
An empirical observation of WikiProjects on the English-language Wikipedia identifies the network properties of the most effective projects.
A simple agent-based model of Network Deliberation shows improvements over conventional deliberation in the presence of strong social influence.
Finally, a controlled experiment studies network deliberation in a real world setting, tracking how individual preferences evolve, and finding evidence that network deliberation provides protection against negative consequences of social influence.
This work seeks to provide a framework that enables an understanding of
of how very large groups can quickly develop a consensus, enabling a more effective use of shared resources to achieve common goals.

>>>>

As groups grow in size, they gain access to additional resources, creating opportunities for collective intelligence and collective action.
However, at very large scales, group decision-making becomes prohibitively slow and difficult to coordinate.
Traditional solutions include representative decision-making and/or a shift from deliberation to voting.
Both approaches sacrifice desirable properties.
Representative decision-making loses the potential benefits of collective intelligence and introduces hierarchies that may place the interests of specific individuals ahead of the interests of the group.
Voting sacrifices generativity: allowing a choice between predefined options, without allowing for improvement to those options.
Arrow’s impossibility theorem also fundamentally limits the fairness of voting.
This project proposes Networked Deliberation as a potential means of effective large-scale decision-making.
In Networked Deliberation, members of a large group are repeatedly partitioned into small deliberative pods.
Overlap between pods at different stages enables group-wide diffusion of information and preferences.
Different methods for assigning members to pods result in different network topologies.
This work combines observational study, agent-based modeling, and an experiment to evaluate and better understand network deliberation.
An empirical observation of WikiProjects on the English-language Wikipedia identifies the network properties of the most effective projects.
A simple agent-based model of Network Deliberation shows improvements over conventional deliberation in the presence of strong social influence.
Finally, a controlled experiment studies network deliberation in a real world setting, tracking how individual preferences evolve, and finding evidence that network deliberation provides protection against negative consequences of social influence.
This work seeks to provide a framework that enables an understanding of
how very large groups can quickly develop a consensus, enabling a more effective use of shared resources to achieve common goals.
